Titeln på avhandlingens språk

### 2022-09-08 model.tex
some formatting

\begin{table}
\centering
\caption[A]{%
    Sample of the execution time data  used for the elaboration of the timing model.
    Rows contain the execution times and \acp{TTF} for each of the \num{169} steps performed by the \num{40} participants in \textcite{olguinmunoz:impact2021}, expressed in seconds, together with a unique identifier for the subject, their associated level of normalized neuroticism, and a sequence number identifying the position of the step in the task.
}\label{tab:data:exectime}
\begin{tabular}{rrrrrr}
    \toprule
    {seq} & {run\_id} & {exec\_time} & {ttf} & {neuroticism}\\
    \midrule
    1 & 134146 & 3.655 & 0.597 & 0.375\\
    2 & 134146 & 4.439 & 0.554 & 0.375\\
    3 & 134146 & 2.943 & 0.562 & 0.375\\
    \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) \\
    169 & 134146 & 3.532 & 4.571 & 0.375\\
    1 & 134470 & 3.461 & 0.561 & 0.594\\
    2 & 134470 & 6.678 & 0.572 & 0.594\\
    \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) \\
    \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) \\
    169 & 137353 & 4.615 & 0.537 & 0.625\\
    \bottomrule
    \end{tabular}
\end{table}

@@

\begin{table*}
\caption{Sample of the processed execution time data table.}\label{tab:data:exectime:processed}
\begin{tabular}{rrrrcrccrc}
\toprule
{seq} & {run\_id} & {next\_exec\_time} & {ttf} & {impairment} & {neuroticism\_raw} & {neuroticism} & {transition} & {duration\_raw} & {duration} \\
\midrule
1   & 134146 & 3.655 & 0.000 & low & 0.375  & low & NoTransition & 1 & short \\
2   & 134146 & 4.439 & 0.597 & low & 0.375 & low & NoTransition & 2 & short \\
3   & 134146 & 2.943 & 0.554 & low & 0.375 & low & NoTransition & 3 & short \\
\( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)\\
169 & 134146 & 3.532 & 3.689 & high & 0.375 & low & Lower2Higher & 2 & short \\
1   & 134470 & 3.461 & 0.000 & low & 0.594 & high & NoTransition & 1 & short \\
2   & 134470 & 6.678 & 0.561 & low & 0.594 & high & NoTransition & 2 & short \\
\( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)\\
\( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)\\
169 & 137353 & 4.615 & 0.579 & low & 0.625 & high & NoTransition & 2 & short \\
\bottomrule
\end{tabular}
\end{table*}

\begin{figure*}
    \centering
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/imp_neur_vs_exectime.png}
        \caption{}\label{fig:timing:impneurvsetime}
    \end{subfigure}%
    \hspace{.05\textwidth}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/duration_vs_exectime.png}
        \caption{}\label{fig:timing:durvsetime}
    \end{subfigure}%
    \hspace{.05\textwidth}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/impairment_transition_vs_exectime.png}
        \caption{}\label{fig:timing:imptransvsetime}
    \end{subfigure}
    \caption{%
        Visualizations of the model data after discretization and post-processing.
        \subref{fig:timing:impneurvsetime} illustrates the effect of impairment on execution times, and how neuroticism modulates this behavior;
        \subref{fig:timing:durvsetime} exemplifies how the model captures the speed-up and slow-down behaviors due to impairment and duration described in \textcite{olguinmunoz:impact2021};
        finally, \subref{fig:timing:imptransvsetime} shows the lingering effects of impairment after a transition.
        Error bars indicate the \SI{95}{\percent} \ac{CI}.
    }\label{fig:timing}
\end{figure*}

>>>>

\begin{table}
    \centering
    \caption[A]{%
        Sample of the execution time data  used for the elaboration of the timing model.
        Rows contain the execution times and \acp{TTF} for each of the \num{169} steps performed by the \num{40} participants in \textcite{olguinmunoz:impact2021}, expressed in seconds, together with a unique identifier for the subject, their associated level of normalized neuroticism, and a sequence number identifying the position of the step in the task.
    }\label{tab:data:exectime}
    \begin{tabular}{rrrrrr}
        \toprule
        {seq}        & {run\_id}    & {exec\_time} & {ttf}        & {neuroticism} \\
        \midrule
        1            & 134146       & 3.655        & 0.597        & 0.375         \\
        2            & 134146       & 4.439        & 0.554        & 0.375         \\
        3            & 134146       & 2.943        & 0.562        & 0.375         \\
        \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)  \\
        169          & 134146       & 3.532        & 4.571        & 0.375         \\
        1            & 134470       & 3.461        & 0.561        & 0.594         \\
        2            & 134470       & 6.678        & 0.572        & 0.594         \\
        \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)  \\
        \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)  \\
        169          & 137353       & 4.615        & 0.537        & 0.625         \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\begin{table*}
    \caption{Sample of the processed execution time data table.}\label{tab:data:exectime:processed}
    \begin{tabular}{rrrrcrccrc}
        \toprule
        {seq}        & {run\_id}    & {next\_exec\_time} & {ttf}        & {impairment} & {neuroticism\_raw} & {neuroticism} & {transition} & {duration\_raw} & {duration}   \\
        \midrule
        1            & 134146       & 3.655              & 0.000        & low          & 0.375              & low           & NoTransition & 1               & short        \\
        2            & 134146       & 4.439              & 0.597        & low          & 0.375              & low           & NoTransition & 2               & short        \\
        3            & 134146       & 2.943              & 0.554        & low          & 0.375              & low           & NoTransition & 3               & short        \\
        \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \)  & \( \cdots \) & \( \cdots \)    & \( \cdots \) \\
        169          & 134146       & 3.532              & 3.689        & high         & 0.375              & low           & Lower2Higher & 2               & short        \\
        1            & 134470       & 3.461              & 0.000        & low          & 0.594              & high          & NoTransition & 1               & short        \\
        2            & 134470       & 6.678              & 0.561        & low          & 0.594              & high          & NoTransition & 2               & short        \\
        \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \)  & \( \cdots \) & \( \cdots \)    & \( \cdots \) \\
        \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \)  & \( \cdots \) & \( \cdots \)    & \( \cdots \) \\
        169          & 137353       & 4.615              & 0.579        & low          & 0.625              & high          & NoTransition & 2               & short        \\
        \bottomrule
    \end{tabular}
\end{table*}

\begin{figure*}
    \centering%
    % \hspace{\fill}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/imp_neur_vs_exectime.png}
        \caption{}\label{fig:timing:impneurvsetime}
    \end{subfigure}%
    \hspace{\fill}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/duration_vs_exectime.png}
        \caption{}\label{fig:timing:durvsetime}
    \end{subfigure}%
    \hspace{\fill}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/impairment_transition_vs_exectime.png}
        \caption{}\label{fig:timing:imptransvsetime}
    \end{subfigure}%
    % \hspace{\fill}%
    \caption{%
        Visualizations of the model data after discretization and post-processing.
        \subref{fig:timing:impneurvsetime} illustrates the effect of impairment on execution times, and how neuroticism modulates this behavior;
        \subref{fig:timing:durvsetime} exemplifies how the model captures the speed-up and slow-down behaviors due to impairment and duration described in \textcite{olguinmunoz:impact2021};
        finally, \subref{fig:timing:imptransvsetime} shows the lingering effects of impairment after a transition.
        Error bars indicate the \SI{95}{\percent} \ac{CI}.
    }\label{fig:timing}
\end{figure*}
